Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-07-23 paper/paper.tex
Splurging out results figures into the draft paper

Fig.\,\ref{f:manip} shows the result of simulating three surgical
manipulations alongside the wildtype result, which is shown on Row A. Rows B
and C show graft rotation simulations (90$\degree$ and 180$\degree$). In each
case an 8x8 square on the tectum (each unit is 0.05x0.05) is rotated. The
rotational sense can be observed clearly in the `Branches' column; for the
90$\degree$ rotation, the top-right (caudal-lateral) corner of the rotated
square is red, whereas the top-left corner of the wildtype tectum is red. \textbf{etc}.

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_manipulations.png}
\caption{Surgical manipulations. Row A: wildtype. Row B: 90 degree
rotation. Row C: 180 degree rotation. Row D: Graft swap.}
\label{f:manip}
\end{figure}

@@

@@

>>>>

Fig.\,\ref{f:surg1} shows the result of simulating three surgical
manipulations alongside the wildtype result, which is shown on Row A. Rows B
and C show graft rotation simulations (90$\degree$ and 180$\degree$). In each
case an 8x8 square on the tectum (each unit is 0.05x0.05) is rotated. The
rotational sense can be observed clearly in the `Branches' column; for the
90$\degree$ rotation, the top-right (caudal-lateral) corner of the rotated
square is red, whereas the top-left corner of the wildtype tectum is red. \textbf{etc}.

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_manipulations.png}
\caption{Surgical manipulations. Row A: wildtype. Row B: 90 degree
rotation. Row C: 180 degree rotation. Row D: Graft swap.}
\label{f:surg1}
\end{figure}

Fig.\,\ref{f:surg2} shows retinal ablation, tectal ablation, mismatch and
compound eye experiments (Stuart: see Simpson and Goodhill Fig. 4).

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_manipulations2.png}
\caption{Surgical manipulations 2. Row A: Retinal ablation, Row B: Tectal
ablation, Row C: Mismatch (ablate retina and also the tectum that matches the
left-behind retina), Row D: Compound eye (Two nasal retinal halves `glued
together')}
\label{f:surg2}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_ephb_wt.png}
\caption{The effect of making one interaction attractive. This models
switching one receptor/ligand pair to be an analogue of EphB, but retains an
assumption that the ephrin-B ligand has exponential form. The change compared
with the model of Fig.\,\ref{f:wt} is that the tectal ligand direction of
$L_1$ is reversed and the interaction of $r_1$ and $L_1$/$l_1$ is made
attractive. $L_1$ retains the assumption of exponential change. Note the
`bunching up' of the field to the medial side of the tectal sheet.}
\label{f:ee_oneattractive}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_eel_ephb_wt.png}
\caption{The arrangement is restored by making the expression of $L_1$ on the
tectal sheet change logarithmically.}
\label{f:eel_oneattractive}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_chemo_manipulations.png}
\caption{Surgical manipulations in the chemoaffinity-only model. Row A: wildtype. Row B: 90 degree
rotation. Row C: 180 degree rotation. Row D: Graft swap}
\label{f:chemosurg}
\end{figure}
